---
title: "20220529_Stability_100gen_killswitchActuators"
author: "Tiffany Halvorsen"
date: "5/29/2022"
output: pdf_document
---

```{r include=FALSE}
library(ggplot2)
library(dplyr)
library(plater)
library(tidyverse)
library(lubridate) #hms function
library(reshape2)
library(ggpubr) #pvalues on ggplpots
library(knitr)
```

```{r echo=FALSE}
theme_tiff <- function(base_size = 12) {
  theme_bw(base_size = base_size) %+replace%
    theme(
      # L'ensemble de la figure
      plot.title = element_text(size = rel(1), face = "bold", margin = margin(0,0,5,0), hjust = 0),
      # Zone où se situe le graphique
      panel.grid.minor = element_blank(),
      panel.border = element_blank(),
      # Les axes
      axis.title = element_text(size = rel(0.85)),
      axis.text = element_text(size = rel(0.70)),
      axis.line = element_line(color = "black"),
      # La légende
      legend.title = element_text(size = rel(0.85)),
      legend.text = element_text(size = rel(0.70)),
      legend.key = element_rect(fill = "transparent", colour = NA),
      legend.key.size = unit(1.5, "lines"),
      legend.background = element_rect(fill = "transparent", colour = NA),
      # Les étiquettes dans le cas d'un facetting
      strip.background = element_rect(fill = "transparent", colour = NA),
      strip.text = element_text(size = rel(0.85), face = "bold", color = "black", margin = margin(5,0,5,0))
    )
}
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Assay
## Grow strains for 50 generations, based off of gen time calculation from 2022 05 25 (included below)
- Inoculate single colonies into 500 uL in LB-kan20-0.1 mM IPTG in deep well plates covered with a plastic 96 well plate lid, taped to the sides  for 24 hours
- Single colonies were isolated from LB-agar containing Kan20 and 1 mM IPTG
- measure starting CFUs and survival ratio (just to check and see if they're detectable yet)
- Measure survival ratio every 24 hrs on 1 mM IPTG and 1 mM cumate LB-agar plates

# Doubling time from 2022 05 25
## Average generation/24 hrs is 10. Grow for 5 days/50 gen.
```{r include=TRUE}
CFUs_pilot <- read_csv(
  "/Users/halvorsen1/Documents/RStudio/csv_files/20220525_StabilityPilot_CFUs.csv")

gen_time <- CFUs_pilot %>%
  group_by(Strain, Replicate) %>%
  mutate(`gen/20hrs` = (log10(CFU_perm[Time==20])-log10(CFU_perm[Time==0]))/log10(2)) %>%
  ungroup() %>%
  group_by(Strain, Time) %>%
  summarise(mean_gen = round(mean(`gen/20hrs`), 2)) %>%
  mutate(`gen/hr` = round(mean_gen/20, 2))

gen_time <- filter(gen_time, Time == "20")

knitr::kable(gen_time,
             caption = "Growth rate and doubling time of strains during pilot experiment")

```

# Starting CFUs (IPTG)

```{r, echo=FALSE}

CFUs_stability <- read_csv("../csv_files/20220531_StabilityAssay_all_killswitches_CFUs.csv")

t0_CFUs <- CFUs_stability %>%
  filter(Time == 0)
t0_CFUs$Strain <- factor(t0_CFUs$Strain,
                         levels = c("TH88", "TH99", "TH100", "TH131", "TH126", "TH240", "TH128", "TH237", "TH124", "TH203"))

strain_names <- as_labeller(c(
                  'TH86' = "regulators only",
                  'TH88' = "CcdB-CcdA",
                  'TH99' = "HicA-HicB",
                  'TH100' = "ParE-ParD",
                  'TH126' = "Tse2-Tsi2",
                  'TH128' = "colicin E2\nImmE2",
                  'TH131' = "RelE-RelB",
                  "TH240" = "Tsi2[ssrA]",
                  "TH237" = "ImmE2[ssrA]",
                  "TH124" = "EcoRI\n(no methylase)",
                  "TH203" = "TisB\n(no antitoxin)"
                  ))

p_t0 <- ggplot(data = t0_CFUs, mapping = aes(x=Replicate, y=log10(CFU_perm))) +
  geom_col() +
  facet_wrap(~Strain, labeller = strain_names, ncol = 10)  +
  labs(title = "Starting CFUs of each strain\n3 replicates each from individual colonies") +
  theme(strip.text.x = element_text(angle = 90))


```


```{r fig.asp = 0.8, fig.width = 6, echo = FALSE}
p_t0 
```


## Survival ratios over  time
### At t=0, cell density was too low to detect escapes on 1 mM cumate

```{r echo=FALSE}

CFUs_stability$Time <- as.numeric(CFUs_stability$Time) / 24
CFUs_stability$Replicate <- as.character(CFUs_stability$Replicate)
CFUs_stability$Strain <- factor(CFUs_stability$Strain,
                         levels = c("TH88", "TH99", "TH100", "TH131", "TH126", "TH240", "TH128", "TH237", "TH124", "TH203"))

strain_names2 <- as_labeller(c(
                  'TH86' = "regulators only",
                  'TH88' = "CcdB-CcdA",
                  'TH99' = "HicA-HicB",
                  'TH100' = "ParE-ParD",
                  'TH126' = "Tse2-Tsi2",
                  'TH128' = "colicin E2\nImmE2",
                  'TH131' = "RelE-RelB",
                  "TH240" = 'Tsi2-ssrA',
                  "TH237" = 'ImmE2-ssrA',
                  "TH124" = "EcoRI\n(no methylase)",
                  "TH203" = "TisB\n(no antitoxin)"
                  ))

p2 <- CFUs_stability %>%
  ggplot(aes(x = Time, y = log10(Escape_freq), color = Strain, shape = Replicate)) +
  geom_point(size = 1) +
  geom_line(size = 0.5) +
  theme_classic() +
  scale_x_continuous(limits = c(0,10), breaks = seq(0,10,1)) +
  geom_hline(yintercept = 0) +
  labs(x = "Time (days)") +
  theme(text = element_text(size = 12),
        strip.background = element_blank(),
        #panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(color = "black", face = "bold", size = 14),
        axis.text = element_text(size = 14), 
        strip.text = element_text(size = 8, vjust = -2, hjust = 0.5),
        legend.position = "right",
        legend.title = element_text(size = 12),
        axis.text.x = element_text(size = 10, vjust = 0.5),
        axis.title.y = element_text(size = 14)
  )
  

```

```{r fig.asp = 0.8, fig.width = 6, echo = FALSE}
p2
```

```{r}

# Plot by kill switch strain

# Take averages to plot overlaid as smooth line with error on top of replicates

std <- function(x) sd(x)/sqrt(length(x))

CFUs_stability_avg <- CFUs_stability %>%
  group_by(Strain, Time) %>%
  summarise(meanEscape_log = log10(mean(Escape_freq)),
            neg_sdEscape_log = -log10(sd(Escape_freq)),
            pos_sdEscape_log = log10(sd(Escape_freq)),
            meanEscape = mean(Escape_freq),
            sdEscape = sd(Escape_freq),
            stdEscape_log = log10(std(Escape_freq)),
            stdEscape = std(Escape_freq)
            )

# Remove T=0 time point

CFUs_stability <- filter(.data = CFUs_stability, Time !=0)
CFUs_stability_avg <- filter(.data = CFUs_stability_avg, Time !=0)


p3 <- CFUs_stability %>%
  ggplot() +
  facet_wrap(~ Strain, labeller = strain_names2, ncol = 10) +
  geom_point( aes(x = Time, y = log10(Escape_freq), color = Strain, shape = Replicate), size = 1) +
  geom_line(aes(x = Time, y = log10(Escape_freq), color = Strain, shape = Replicate), size = 0.5) +
  geom_smooth(aes(x=Time, y=log10(Escape_freq), color=Strain)) +
  theme_classic() +
  scale_x_continuous(limits = c(1,10), breaks = c(0,2,4,6,8,10)) +
  scale_color_manual(values = c("TH86" = "gray",
                                "TH88" = "#EC5E8D",
                                "TH99" = "purple",
                                "TH100" = "#E0D935",
                                "TH131" = "#F7AB37",
                                "TH126" = "#36D81C",
                                "TH128" = "#4796F5",
                                "TH98" = "#30ECEC",
                                "TH124" = "#30ECEC",
                                "TH203" = "#D4BFDB",
                                "TH214" = "#D4BFDB",
                                "TH240" = "#40A636",
                                "TH237" = "#4180C9")) +  
  geom_hline(yintercept = 0) +
  labs(x = "Time (days)",
       y=expression('log'[10]*' survival ratio')) +
  theme(
        strip.background = element_blank(),
        panel.grid.major.y = element_line(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(color = "black", face = "bold", size = 14),
        axis.text = element_text(size = 12), 
        #strip.text = element_text(size = 8, vjust = -2, hjust = 0.5),
        strip.text = element_text(size = 8, vjust = -0.05, hjust= 0.5),
        legend.position = "none",
        legend.title = element_text(size = 12),
        axis.text.x = element_text(size = 12, vjust = 0.5),
        axis.title = element_text(size = 14)
  )


```

```{r fig.asp = 0.5, fig.width = 7, fig.height = 2.5, echo = FALSE}
p3
```


```{r, include=FALSE}
ggsave(filename = "20220609_Stability_100gen_poster.png", path = "/Users/halvorsen1/Documents/R_graphs/Escape_mutants", width = 17, height = 2.7, units = "in", device='png', dpi=300)
```