---
title: "20220527_Stability_killswitches_SBW25"
author: "Tiffany Halvorsen"
date: "5/27/2022"
output: pdf_document
---

```{r include=FALSE}
library(ggplot2)
library(dplyr)
library(plater)
library(tidyverse)
library(lubridate) #hms function
library(reshape2)
library(ggpubr) #pvalues on ggplpots
library(knitr)
```

```{r echo=FALSE}
theme_tiff <- function(base_size = 12) {
  theme_bw(base_size = base_size) %+replace%
    theme(
      # L'ensemble de la figure
      plot.title = element_text(size = rel(1), face = "bold", margin = margin(0,0,5,0), hjust = 0),
      # Zone où se situe le graphique
      panel.grid.minor = element_blank(),
      panel.border = element_blank(),
      # Les axes
      axis.title = element_text(size = rel(0.85)),
      axis.text = element_text(size = rel(0.70)),
      axis.line = element_line(color = "black", arrow = arrow(length = unit(0.3, "lines"), type = "closed")),
      # La légende
      legend.title = element_text(size = rel(0.85)),
      legend.text = element_text(size = rel(0.70)),
      legend.key = element_rect(fill = "transparent", colour = NA),
      legend.key.size = unit(1.5, "lines"),
      legend.background = element_rect(fill = "transparent", colour = NA),
      # Les étiquettes dans le cas d'un facetting
      strip.background = element_rect(fill = "#17252D", color = "#17252D"),
      strip.text = element_text(size = rel(0.85), face = "bold", color = "white", margin = margin(5,0,5,0))
    )
}
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Pilot Experiment
### Grow strains for 48 hours, calculate doubling time and escape 3x
- Grow 500 uL overnight cultures in 5 mL plastic culture tubes from single colonies grown on LB-kan20-1 mM IPTG for 24 hours
- Inoculate into 96 deep well plate 1:1000 into LB-kan-0.1 mM IPTG
- measure starting CFUs and survival ratio
- Measure CFUs again in the morning to get growth rate during linear part of the ln transformed curve (hopefully)
- Measure survival ratio at 24 and 48 hrs to get an idea of how dense the culture gets each day

### Doubling time
```{r include=TRUE}
CFUs_pilot <- read_csv(
  "/Users/halvorsen1/Documents/RStudio/csv_files/20220525_StabilityPilot_CFUs.csv")

gen_time <- CFUs_pilot %>%
  group_by(Strain, Replicate) %>%
  mutate(`gen/20hrs` = (log10(CFU_perm[Time==20])-log10(CFU_perm[Time==0]))/log10(2)) %>%
  ungroup() %>%
  group_by(Strain, Time) %>%
  summarise(mean_gen = round(mean(`gen/20hrs`), 2)) %>%
  mutate(`gen/hr` = round(mean_gen/20, 2))

gen_time <- filter(gen_time, Time == "20")

knitr::kable(gen_time,
             caption = "Growth rate and doubling time of strains during pilot experiment")

```

## Starting CFUs (IPTG)
### This was a 1:1000 dilution of an overnight culture into 500 uL LB (0.5 uL) in 96 well deep well plate

**Will do the actual assay by seeding 96 well plate wells from single colonies grown for 24 hours

```{r, echo=FALSE}

t0_CFUs <- CFUs_pilot %>%
  filter(Time == 0) %>%
  group_by(Strain) %>%
  summarise(meanCFU = mean(CFU_perm),
            sdCFU = sd(CFU_perm))
t0_CFUs$Strain <- factor(t0_CFUs$Strain,
                         levels = c("TH88", "TH99", "TH100", "TH131", "TH126", "TH240", "TH128", "TH237", "TH245"))

p <- ggplot(data = t0_CFUs, mapping = aes(x=Strain, y=meanCFU)) +
  geom_col() +
  geom_errorbar(aes(ymin = meanCFU-sdCFU, ymax = meanCFU+sdCFU), width = 0.5) +
  scale_y_log10()
  

```


```{r fig.asp = 0.8, fig.width = 4}
p + theme_tiff()
```


## Survival ratios over 48 hrs
### At t=0, cell density was too low to detect escapes on 1 mM cumate

```{r echo=FALSE}

CFUs_pilot$Time <- as.character(CFUs_pilot$Time)
p2 <- CFUs_pilot %>%
  filter(Time != '0' & Time != '20') %>%
  ggplot(data = CFUs_pilot, mapping = aes(x = Strain, y = log10(Escape_freq), color = Time)) +
  geom_point(size = 1.5) +
  theme_classic() +
  geom_hline(yintercept = 0) +
  theme(text = element_text(size = 12),
        strip.background = element_blank(),
        #panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(color = "black", face = "bold", size = 14),
        axis.text = element_text(size = 14), 
        strip.text = element_text(size = 8, vjust = -2, hjust = 0.5),
        legend.position = "right",
        legend.title = element_text(size = 12),
        axis.text.x = element_text(size = 10, angle = 90, vjust = 0.5, hjust = 0.95),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 14)
  )
  

```

```{r fig.asp = 0.8, fig.width = 6}
p2
```
