---
title: "20220708_TH87_MinimalMedia_FoldChanges"
author: "Tiffany Halvorsen"
date: '2022-07-11'
output: pdf_document
---


```{r, include = FALSE}
library(ggplot2)
library(dplyr)
library(plater)
library(tidyverse)
library(lubridate) #hms function
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
TH87_KEYS <- read_plate("/Users/halvorsen1/Documents/RStudio/csv_files/20220708_TH87_MinimalMedia _foldChanges_KEYS.csv", well_ids_column = "Key")

TH87_OD <- pivot_longer(read_csv("/Users/halvorsen1/Documents/RStudio/csv_files/20220708_TH87_MinimalMedia _foldChanges_OD.csv"),
                                 cols = A01:H12,
                                 names_to = "Key",
                                 values_to = "OD600"
                                 )

TH87_GFP <- pivot_longer(read_csv("/Users/halvorsen1/Documents/RStudio/csv_files/20220708_TH87_MinimalMedia _foldChanges_GFP.csv"),
                         cols = A01:H12,
                         names_to = "Key",
                         values_to = "GFP"
                         )

TH87_mRuby2 <- pivot_longer(read_csv("/Users/halvorsen1/Documents/RStudio/csv_files/20220708_TH87_MinimalMedia _foldChanges_mRuby2.csv"),
                            cols = A01:H12,
                            names_to = "Key",
                            values_to = "mRuby2"
                            )

#Combine fluorescence with OD600
TH87_GFP_OD <- cbind(TH87_OD, TH87_GFP[3])
TH87_mRuby2_OD <- cbind(TH87_OD, TH87_mRuby2[3])

#Reformat time, plus adjust for time plate was in benchtop shaker prior to overnight growth in reader
y <- hms(TH87_GFP_OD$`Time`)
TH87_GFP_OD$`Time` <- round(hour(y) + minute(y) / 60 + second(y) / 360, digits = 2) + 3.5
y <- hms(TH87_mRuby2_OD$`Time`)
TH87_mRuby2_OD$`Time` <- round(hour(y) + minute(y) / 60 + second(y) / 360, digits = 2) + 3.5

#Add keys
TH87_GFP_OD <- full_join(TH87_GFP_OD, TH87_KEYS)
TH87_mRuby2_OD <- full_join(TH87_mRuby2_OD, TH87_KEYS)

#Calculate fluorescence relative to OD
TH87_GFP_OD <- TH87_GFP_OD %>%
  filter(Inducer == 'IPTG') %>%
  mutate('GFP/OD' = GFP/OD600)
TH87_mRuby2_OD <- TH87_mRuby2_OD %>%
  filter(Inducer == "cumate") %>%
  mutate('mRuby2/OD' = mRuby2/OD600)

# Pick one time point for comparison
TH87_GFP_OD
```



```{r, echo=FALSE}

TH87_GFP_OD$Media <- factor(TH87_GFP_OD$Media,
                            levels = c("LB",
                                       "Succinate",
                                       "Proline",
                                       "Glucose"))

p1 <- ggplot() +
  geom_point(data = TH87_GFP_OD, aes(x = `Time`, y = `GFP/OD`), color = "darkgreen") + 
  facet_grid(Media ~ Concentration)


```
# GFPmut3b fluorescence over time as a function of media composition and inducer level
```{r fig.asp = 0.7, fig.width = 6, echo = FALSE}
p1
```
<br>
<br>
<br>
<br>

```{r, echo=FALSE}
TH87_mRuby2_OD$Media <- factor(TH87_mRuby2_OD$Media,
                            levels = c("LB",
                                       "Succinate",
                                       "Proline",
                                       "Glucose"))
p2 <- ggplot() +
  geom_point(data = TH87_mRuby2_OD, aes(x = `Time`, y = `mRuby2/OD`), color = "darkred") + 
  facet_grid(Media ~ Concentration)
```
# mRuby2 fluorescence over time as a function of media composition and inducer level
```{r fig.asp = 0.7, fig.width = 6, echo = FALSE}
p2
```

\newpage

```{r, include=FALSE}
TH87_GFP_OD$Media <- factor(TH87_GFP_OD$Media,
                            levels = c("LB",
                                       "Succinate",
                                       "Proline",
                                       "Glucose"))

p3 <- TH87_GFP_OD %>%
  filter(Time == 15.53) %>%
  ggplot() +
  geom_point(aes(x = `Concentration`, y = `GFP/OD`), color = 'darkgreen') + 
  facet_wrap(~Media, ncol = 4, nrow = 1) +  
  scale_x_log10() +
  scale_y_log10() +
  geom_smooth(aes(x=Concentration, y=`GFP/OD`), method = 'loess', span = 1.5, se = FALSE, color = 'green') +
  theme(
    axis.text.x = element_text(size = 6)
  )
```
# Fold change of Ptac at 15.5 hrs post-inoculation
```{r fig.asp = 0.4, fig.width = 6, echo = FALSE}
p3
```




```{r, include=FALSE}
TH87_mRuby2_OD$Media <- factor(TH87_mRuby2_OD$Media,
                            levels = c("LB",
                                       "Succinate",
                                       "Proline",
                                       "Glucose"))

p4 <- TH87_mRuby2_OD %>%
  filter(Time == 15.53) %>%
  ggplot() +
  geom_point(aes(x = `Concentration`, y = `mRuby2/OD`), color = 'darkred') + 
  facet_wrap(~Media, ncol = 4, nrow = 1) +  
  scale_x_log10() +
  scale_y_log10() +
  geom_smooth(aes(x=Concentration, y=`mRuby2/OD`), method = 'loess', span = 1.5, se = FALSE, color = 'red') +
    theme(
    axis.text.x = element_text(size = 6)
  )
```
# Fold change of Pcym at 15.5 hrs post-inoculation
```{r fig.asp = 0.4, fig.width = 6, echo = FALSE}
p4
```


\newpage

```{r include = FALSE}

TH87_GFP_OD_means <- TH87_GFP_OD %>%
  group_by(Media, Time) %>%
  summarise_at(.vars = vars(`OD600`), .funs = c(meanOD = mean, sdOD =sd))

TH87_GFP_OD_means$Media <- factor(TH87_GFP_OD_means$Media, 
                                  levels = c("LB",
                                             "Succinate",
                                             "Proline",
                                             "Glucose"))
p5 <- TH87_GFP_OD_means %>%
  ggplot() +
  geom_point(aes(x = `Time`, y = `meanOD`), color = 'darkgreen') + 
  geom_errorbar(aes(x = `Time`, y = `meanOD`, ymin = meanOD-sdOD, ymax = meanOD+sdOD)) +
  facet_wrap(~Media, ncol = 4, nrow = 1) +  
  theme(
    axis.text.x = element_text(size = 10)
  )

```
\newpage


# Growth of SBW25 reporter strain in minimal media in plate reader (IPTG samples)
* Both promoters are less active in proline, which is due to decreased growth (never entered log phase).
* In contrast, the minimal-succinate samples are in log phase at 15 hrs, and there is different activity from either promoter.
  + 15 hrs also mimics overnight growth, as in the escape mutant selections/survival raito analyses. 
  + Although the minimal-glucose samples also have different promoter activities (less output in glucose from Ptac compared to in LB), these samples also have a much higher growth rate than those growing in succinate. So, both glucose and succinate exhibit decreased sensitivity to IPTG induction yet very different growth rates. One interpretation of the EcoRI-RIM data, then, is that a slower growth rate combined with decreased Ptac expression increases Pcym-EcoRI toxicity in minimal-succinate (less opportunity for methylation + less repliation to produce new WT copies to mediate recombination repair).
      - Could also be entirely metabolic burden, but I am surprised decreased survival doesn't occur in proline (unless all are escapes..)
      - For other toxins, the slight increase in survival ratio likely represents stronger selection against circuit function either because Pcym >> Ptac or increased metabolic burden selects against function (as we stated previously).
      

```{r fig.asp = 0.3, fig.width = 6, echo = FALSE}
p5
```


```{r include = FALSE}

TH87_mRuby2_OD_means <- TH87_mRuby2_OD %>%
  group_by(Media, Time) %>%
  summarise_at(.vars = vars(`OD600`), .funs = c(meanOD = mean, sdOD =sd))

TH87_mRuby2_OD_means$Media <- factor(TH87_mRuby2_OD_means$Media, 
                                  levels = c("LB",
                                             "Succinate",
                                             "Proline",
                                             "Glucose"))
p6 <- TH87_mRuby2_OD_means %>%
  ggplot() +
  geom_point(aes(x = `Time`, y = `meanOD`), color = 'darkred') + 
  geom_errorbar(aes(x = `Time`, y = `meanOD`, ymin = meanOD-sdOD, ymax = meanOD+sdOD)) +
  facet_wrap(~Media, ncol = 4, nrow = 1) +  
  theme(
    axis.text.x = element_text(size = 10)
  )

```

# Growth of SBW25 reporter strain in minimal media in plate reader (cumate samples)
+ Same decreased growth occurs for both inducers, regardless of concentration.

```{r fig.asp = 0.3, fig.width = 6, echo = FALSE}
p6
```

