---
title: "-outs: both in the same plate, with a second plate control (no inducers post washout)"
output: html_notebook
---

```{r}
library(ggplot2)
library(dplyr)
library(plater)
library(tidyverse)
library(lubridate) #hms function
library(reshape2)
```

```{r}
washout_CFUs <- read.csv(file = "/Users/halvorsen1/Documents/RStudio/csv_files/20220420_TA_bothWashouts_Escapes.csv")

washout_CFUs$Strain <-factor(washout_CFUs$Strain,
                  levels = c("TH88", "TH99", "TH100", "TH131"))

washout_CFUs$Pre_washout <-factor(washout_CFUs$Pre_washout,
                  levels = c("no cumate", "0.07 mM cumate", "0.3 mM cumate", "no IPTG", "0.3 mM IPTG", "0.7 mM IPTG"))

strain_names <- c("TH88" = "CcdB-CcdA",
                              "TH99" = "HicA-HicB",
                              "TH100" = "ParE-ParD",
                              "TH131" = "RelE-RelB")

washout_CFUs %>%
  filter(Time != 5 & Time != 0) %>%
  filter(Post_washout == "1 mM IPTG") %>%
  ggplot(aes(x = as.character(Time), y = Escape_freq, fill = Strain)) +
  geom_bar(position = "dodge",
           stat = "identity",
           size = 1, 
           color = "black") +
  facet_grid(~ Pre_washout, space = "free_x", scales = "free_x", switch="x") +
  labs(y="survival ratio",
       x = "IPTG",
       title = "Expt washout: cumate into IPTG") +
  scale_fill_manual(values = c("TH88" = "#EC5E8D",
                                "TH99" = "#DAA9ED",
                               "TH100" = "#E0D935",
                               "TH131" = "#F7AB37"),
                     labels = strain_names) +

  scale_y_log10(
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", scales::math_format(10^.x))) +
  #geom_vline(xintercept = c(1.5), size = 0.5) +
  geom_hline(yintercept = 1, color = "black") +
  theme_classic() +
  theme(text = element_text(size = 12),
        strip.background = element_blank(),
        panel.spacing.x = unit(2, "lines"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(color = "black", face = "bold", size = 11),
        axis.text = element_text(size = 14), 
        strip.text = element_text(face = "bold", size = 10),
        legend.position = "right",
        legend.title = element_blank(),
        axis.text.x = element_text(size = 12),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 14)
        )



```

```{r}
ggsave(filename = "20220422_TAs_IPTG_washout_Escape_Plate2_t24.png", path = "/Users/halvorsen1/Documents/R_graphs/Escape_mutants", width = 9, height = 4, units = "in", device='png', dpi=300)
```

washout_CFUs <- aggregate(washout_CFUs, by = list(washout_CFUs$))

Plot raw CFUs instead of ratio

```{r}
washout_CFUs_long <- read_csv(file = "/Users/halvorsen1/Documents/RStudio/csv_files/20220421_escapeFrequencies_TA_washouts_long.csv")
washout_CFUs_long$Selection <-factor(washout_CFUs_long$Selection,
                  levels = c("permissive", "nonpermissive"))
washout_CFUs_long$Strain <-factor(washout_CFUs_long$Strain,
                  levels = c("TH88", "TH99", "TH100", "TH131"))
washout_CFUs_long$Pre_washout <-factor(washout_CFUs_long$Pre_washout,
                  levels = c("no cumate", "0.07 mM cumate", "0.3 mM cumate", "no IPTG", "0.3 mM IPTG", "0.7 mM IPTG"))

strain_names <- as_labeller(c("TH88" = "CcdB\nCcdA",
                              "TH99" = "HicA\nHicB",
                              "TH100" = "ParE\nParD",
                              "TH131" = "RelE\nRelB"))



washout_CFUs_long %>%
  filter(Time != '5' & Post_washout == "no IPTG" & Time == "19" & Pre_washout != "0.07 mM cumate") %>%
  group_by(Selection, Strain) %>%
  ggplot(aes(x = Selection, y = CFU, fill = Pre_washout)) +
  geom_bar(position = "dodge",
           stat = "identity") +
  facet_grid(~ Strain, labeller = strain_names, space = "free_x", scales = "free_x", switch="x") +
  labs(y="CFU/mL",
       legend = "Pre-wash\ntreatment",
       title = "Control: no IPTG post-wash, Last time point") +
  scale_fill_manual(values = c("no cumate" = "grey",
                                "0.3 mM cumate" = "darkred"
                                )) +
  scale_y_log10(
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", scales::math_format(10^.x))) +
  #scale_x_discrete(labels = strain_names) +
  geom_vline(xintercept = c(5.5, 7.5), size = 0.3) +
  geom_hline(yintercept = 1, color = "black") +
  theme_classic() +
  theme(text = element_text(size = 12),
        strip.background = element_blank(),
        panel.spacing.x = unit(2, "lines"),
        panel.grid.major.y = element_line(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(color = "black", face = "bold", size = 11),
        axis.text = element_text(size = 12), 
        strip.text = element_text(face = "bold", size = 9),
        legend.position = "right",
        legend.title = element_text(size = 12),
        axis.text.x = element_text(angle = 90, size = 9, vjust = .2, hjust = 0.95),
        axis.title.x = element_blank())

```
```{r}
ggsave(filename = "20220422_TA_washouts_CFUs_CTRL_t19.png", path = "/Users/halvorsen1/Documents/R_graphs/Escape_mutants", width = 7.5, height = 4.5, units = "in", device='png', dpi=300)
```


Control Plate (Plate1, ran in HTX)

```{r}
plate1_outgrowth <- read_csv(file = "/Users/halvorsen1/Documents/RStudio/csv_files/20220420_TA_bothWashouts_Plate1_outgrowth.csv")
plate1_washout <- read_csv(file = "/Users/halvorsen1/Documents/RStudio/csv_files/20220420_TA_bothWashouts_Plate1_washout.csv")
plate1_keys <- read_plate(
  "/Users/halvorsen1/Documents/RStudio/csv_files/20220420_TA_bothWashouts_Plate1_KEYS.csv",
  well_ids_column = "Key")

plate1_outgrowth <- pivot_longer(plate1_outgrowth, cols = A01:H12, names_to = "Key", values_to = "OD600")
plate1_washout <- pivot_longer(plate1_washout, cols = A01:H12, names_to = "Key", values_to = "OD600")

#Reformat time
y <- hms(plate1_outgrowth$`Time`)
plate1_outgrowth$`Time` <- hour(y) + minute(y) / 60 + second(y) / 360

y <- hms(plate1_washout$`Time`)
plate1_washout$`Time` <- hour(y) + minute(y) / 60 + second(y) / 360

plate1_washout$Time <- round(plate1_washout$Time + 6.5, digits = 2)

plate1 <- rbind(plate1_outgrowth, plate1_washout)

plate1 <- full_join(plate1, plate1_keys, by = "Key")
```


Control Plate, cumate washout:

```{r}
plate1_cum <- plate1 %>%
  filter(washout == 'cumate') %>%
  group_by(Strain, `cumate (mM)`, Time) %>%
  summarise_at(.vars = "OD600", .funs = c(meanOD = mean, sdOD = sd))

# Plot both outgrowth and washout together on 1 graph

strain_names <- as_labeller(c(
                  'TH88' = "CcdB-CcdA",
                  'TH99' = "HicA-HicB",
                  'TH100' = "ParE-ParD",
                  'TH131' = "RelE-RelB"))

plate1_cum$Strain <- factor(plate1_cum$Strain,
                         levels = c("TH88", "TH99", "TH100", "TH131"))

cumate_vals <- c(0,0.02,0.07,0.1,0.3,0.5)
discrete_cum <- c("#DBC873", "#C2A464", "#C8B09D", "#AD8E97", "#AC75C1", "#A442C9", "#A442C9")
plate1_cum$`cumate (mM)`<- as.factor(plate1_cum$`cumate (mM)`)

plate2_cum %>% 
  filter(`cumate (mM)` == 0 | `cumate (mM)` == 0.07 | `cumate (mM)` == 0.3) %>%
  ggplot(aes(x = Time, y = meanOD, color = `Strain` , group = `Strain`)) +
  facet_wrap(facets = vars(`cumate (mM)`), nrow = 5, ncol = 6) +
  geom_rect(xmin=-.3, 
            xmax=5.5, 
            ymin=-.25, 
            ymax=max(plate1_cum$Time),
            color = NA,
            fill = "gray93", 
            alpha = 0.5) +
  geom_line(size = 0.5) +  
  geom_point(size = 1) +
  geom_errorbar(aes(ymin = meanOD-sdOD, ymax = meanOD+sdOD), width = 0.5) +
  scale_color_manual(values = c("TH88" = "#EC5E8D",
                                "TH99" = "#DAA9ED",
                               "TH100" = "#E0D935",
                               "TH131" = "#F7AB37"),
                     labels = strain_names) +
  labs(x = 'Time (hrs)', 
       y = expression('OD'[600]),
       title = "Experimental washout: cumate washout into IPTG") +
  scale_x_continuous(limits = c(0,25), breaks = seq(0,25,4)) +
  scale_y_continuous(limits = c(0,2), breaks = seq(0,2,0.5)) +
  #scale_color_gradient(low = "#DCCC15", 
  #                     high = "#876493",
  #                     guide = "legend", 
  #                     aesthetics = "color", 
  #                     values = cumate_vals,
  #                     na.value = NA) +
  #scale_colour_brewer(palette = "spectral", direction = -1) +
  theme_bw() +
  theme(strip.background = element_blank(),
        #strip.text.x = element_text(face = "bold", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 13),
        plot.title = element_text(size = 13, color = "black", face = "bold"),
        legend.text = element_text(size = 14),
        legend.title = element_blank(),
        strip.text.x = element_text(size = 12),
        legend.key.size = unit(0.8, 'cm'),
        axis.title = element_text(size = 14)
          )

```
```{r}
ggsave(filename = "20220420_TAs_cum_washout_Plate2_FigS4.png", path = "/Users/halvorsen1/Documents/R_graphs/Washouts", width = 9, height = 3, units = "in", device='png', dpi=300)
```


Control Plate, IPTG washout:

```{r}
plate1_IPTG <- plate1 %>%
  filter(washout == 'IPTG') %>%
  group_by(Strain, `IPTG (mM)`, Time) %>%
  summarise_at(.vars = "OD600", .funs = c(meanOD = mean, sdOD = sd))

# Plot both outgrowth and washout together on 1 graph

strain_names <- as_labeller(c(
                  'TH88' = "CcdB-CcdA",
                  'TH99' = "HicA-HicB",
                  'TH100' = "ParE-ParD",
                  'TH131' = "RelE-RelB"))

plate1_IPTG$Strain <- factor(plate1_IPTG$Strain,
                         levels = c("TH88", "TH99", "TH100", "TH131"))

discrete_IPTG <- c("#A442C9", "#AC75C1", "#AD8E97", "#C8B09D", "#C2A464", "#DBC873")
plate1_IPTG$`IPTG (mM)`<- as.factor(plate1_IPTG$`IPTG (mM)`)

plate1_IPTG %>% 
  #filter(`IPTG (mM)` == 0) %>%
  ggplot(aes(x = Time, y = meanOD, color = `Strain` , group = `Strain`)) +
  facet_wrap(facets = vars(`IPTG (mM)`), nrow = 5, ncol = 6) +
  geom_rect(xmin=-.3, 
            xmax=5.5, 
            ymin=-.25, 
            ymax=max(plate1_cum$Time),
            color = NA,
            fill = "gray93", 
            alpha = 0.5) +
  geom_line(size = 0.5) +  
  geom_point(size = 1) +
  geom_errorbar(aes(ymin = meanOD-sdOD, ymax = meanOD+sdOD), width = 0.5) +
  scale_color_manual(values = c("TH88" = "#EC5E8D",
                                "TH99" = "#DAA9ED",
                               "TH100" = "#E0D935",
                               "TH131" = "#F7AB37"),
                     labels = strain_names) +
  labs(x = 'Time (hrs)', 
       y = expression('OD'[600]),
       title = "Control washout: IPTG washout into LB") +
  scale_x_continuous(limits = c(0,25), breaks = seq(0,25,4)) +
  scale_y_continuous(limits = c(0,2), breaks = seq(0,2,0.5)) +
  #scale_color_gradient(low = "#DCCC15", 
  #                     high = "#876493",
  #                     guide = "legend", 
  #                     aesthetics = "color", 
  #                     values = cumate_vals,
  #                     na.value = NA) +
  #scale_colour_brewer(palette = "spectral", direction = -1) +
  theme_bw() +
  theme(strip.background = element_blank(),
        #strip.text.x = element_text(face = "bold", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 16),
        plot.title = element_text(size = 13, color = "black", face = "bold"),
        legend.text = element_text(size = 14),
        legend.title = element_blank(),
        strip.text.x = element_text(size = 12),
        legend.key.size = unit(0.8, 'cm'),
        axis.title = element_text(size = 14)
          )
```

```{r}
ggsave(filename = "20220420_TAs_IPTG_washout_Plate1_ALL.png", path = "/Users/halvorsen1/Documents/R_graphs/Washouts", width = 14, height = 3, units = "in", device='png', dpi=300)
```

Experimental Plate (Plate2, ran in H1)

```{r}
plate2_outgrowth <- read_csv(file = "/Users/halvorsen1/Documents/RStudio/csv_files/20220420_TA_bothWashouts_plate2_outgrowth.csv")
plate2_washout <- read_csv(file = "/Users/halvorsen1/Documents/RStudio/csv_files/20220420_TA_bothWashouts_plate2_washout.csv")
plate2_keys <- read_plate(
  "/Users/halvorsen1/Documents/RStudio/csv_files/20220420_TA_bothWashouts_plate2_KEYS.csv",
  well_ids_column = "Key")

plate2_outgrowth <- pivot_longer(plate2_outgrowth, cols = A01:H12, names_to = "Key", values_to = "OD600")
plate2_washout <- pivot_longer(plate2_washout, cols = A01:H12, names_to = "Key", values_to = "OD600")

#Reformat time
y <- hms(plate2_outgrowth$`Time`)
plate2_outgrowth$`Time` <- hour(y) + minute(y) / 60 + second(y) / 360

y <- hms(plate2_washout$`Time`)
plate2_washout$`Time` <- hour(y) + minute(y) / 60 + second(y) / 360

plate2_washout$Time <- round(plate2_washout$Time + 6.5, digits = 2)

plate2 <- rbind(plate2_outgrowth, plate2_washout)

plate2 <- full_join(plate2, plate2_keys, by = "Key")
```


Experimental Plate, cumate washout:

```{r}
plate2_cum <- plate2 %>%
  filter(washout == 'cumate') %>%
  group_by(Strain, `cumate (mM)`, Time) %>%
  summarise_at(.vars = "OD600", .funs = c(meanOD = mean, sdOD = sd))

plate2_cum <- filter(.data = plate2_cum, Strain == "TH88" | Strain == "TH99" | Strain == "TH100" | Strain == "TH131")

# Plot both outgrowth and washout together on 1 graph

strain_names <- as_labeller(c(
                  'TH88' = "CcdB-CcdA",
                  'TH99' = "HicA-HicB",
                  'TH100' = "ParE-ParD",
                  'TH131' = "RelE-RelB"))

plate2_cum$Strain <- factor(plate2_cum$Strain,
                         levels = c("TH88", "TH99", "TH100", "TH131"))

cumate_vals <- c(0,0.02,0.07,0.1,0.3,0.5)
discrete_cum <- c("#DBC873", "#C2A464", "#C8B09D", "#AD8E97", "#AC75C1", "#A442C9", "#A442C9")
plate2_cum$`cumate (mM)`<- as.factor(plate2_cum$`cumate (mM)`)

plate2_cum %>% 
  ggplot(aes(x = Time, y = meanOD, color = `cumate (mM)` , group = `cumate (mM)`)) +
  facet_wrap(facets = vars(Strain), labeller = strain_names, nrow = 5, ncol = 6) +
  geom_rect(xmin=-.3, 
            xmax=5, 
            ymin=-.25, 
            ymax=max(plate2_cum$Time),
            color = NA,
            fill = "gray93", 
            alpha = 0.5) +
  geom_line(size = 0.5) +  
  geom_point(size = 1) +
  geom_errorbar(aes(ymin = meanOD-sdOD, ymax = meanOD+sdOD), width = 0.2) +
  labs(x = 'Time (hrs)', 
       y = expression('OD'[600]),
       color = "cumate (mM)\nduring outgrowth",
       title = "") +
  scale_x_continuous(limits = c(0,25), breaks = seq(0,25,4)) +
  scale_y_continuous(limits = c(0,2), breaks = seq(0,2,0.5)) +
  # scale_color_manual(values = c("TH88" = "#EC5E8D",
  #                               "TH99" = "#DAA9ED",
  #                              "TH100" = "#E0D935",
  #                              "TH131" = "#F7AB37"),
  #                    labels = strain_names) +
  #scale_color_gradient(low = "#DCCC15", 
  #                     high = "#876493",
  #                     guide = "legend", 
  #                     aesthetics = "color", 
  #                     values = cumate_vals,
  #                     na.value = NA) +
  #scale_colour_brewer(palette = "spectral", direction = -1) +
  scale_color_manual(values=discrete_cum) +
  theme_bw() +
  theme(strip.background = element_blank(),
        #strip.text.x = element_text(face = "bold", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 10),
        text = element_text(size = 12),
        plot.title = element_text(size = 13, color = "black", face = "bold"),
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 9),
        strip.text.x = element_text(size = 12),
        legend.key.size = unit(0.4, 'cm')
        )
```

```{r}
ggsave(filename = "20220420_TAs_cum_washout_Plate2_ALL_FIG.png", path = "/Users/halvorsen1/Documents/R_graphs/Washouts", width = 10, height = 2.7, units = "in", device='png', dpi=300)
```


Experimental Plate, IPTG washout:

```{r}
plate2_IPTG <- plate2 %>%
  filter(washout == 'IPTG') %>%
  group_by(Strain, `IPTG (mM)`, Time) %>%
  summarise_at(.vars = "OD600", .funs = c(meanOD = mean, sdOD = sd))

strain_names <- as_labeller(c(
                  'TH88' = "CcdB-CcdA",
                  'TH99' = "HicA-HicB",
                  'TH100' = "ParE-ParD",
                  'TH131' = "RelE-RelB"))

plate2_IPTG$Strain <- factor(plate2_IPTG$Strain,
                         levels = c("TH88", "TH99", "TH100", "TH131"))

discrete_IPTG <- c("#A442C9", "#AC75C1", "#AD8E97", "#C8B09D", "#C2A464", "#DBC873")
plate2_IPTG$`IPTG (mM)`<- as.factor(plate2_IPTG$`IPTG (mM)`)

plate2_IPTG %>% 
  #filter(`IPTG (mM)` == 0.7) %>%
  ggplot(aes(x = Time, y = meanOD, color = `IPTG (mM)` , group = `IPTG (mM)`)) +
  facet_wrap(facets = vars(`Strain`), labeller = strain_names, nrow = 5, ncol = 6) +
  geom_rect(xmin=-.3, 
            xmax=5, 
            ymin=-.25, 
            ymax=max(plate2$Time),
            color = NA,
            fill = "gray93", 
            alpha = 0.5) +
  geom_line(size = 0.5) +  
  #guides(color = "none") +
  geom_point(size = 1) +
  #scale_shape_manual(values=c(15, 16, 17, 18, 3, 4, 8)) +
  geom_errorbar(aes(ymin = meanOD-sdOD, ymax = meanOD+sdOD), width = 0.2) +
  labs(x = 'Time (hrs)', 
       y = expression('OD'[600]),
       color = "IPTG (mM)\nduring outgrowth",
       title = "Experimental plate: IPTG washout with 1 mM cumate addition") +
  scale_x_continuous(limits = c(0,25), breaks = seq(0,25,4)) +
  scale_y_continuous(limits = c(0,2), breaks = seq(0,2,0.5)) +
  #scale_color_gradient(low = "#DCCC15", 
  #                     high = "#876493",
  #                     guide = "legend", 
  #                     aesthetics = "color", 
  #                     values = cumate_vals,
  #                     na.value = NA) +
  #scale_colour_brewer(palette = "spectral", direction = -1) +
  scale_color_manual(values=discrete_cum) +
  # scale_color_manual(values = c("TH88" = "#EC5E8D",
  #                               "TH99" = "#DAA9ED",
  #                              "TH100" = "#E0D935",
  #                              "TH131" = "#F7AB37"),
  #                    labels = strain_names) +
  theme_bw() +
  theme(strip.background = element_blank(),
        #strip.text.x = element_text(face = "bold", size = 12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 10),
        text = element_text(size = 12),
        plot.title = element_text(size = 13, color = "black", face = "bold"),
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 9),
        strip.text.x = element_text(size = 12),
        legend.key.size = unit(0.4, 'cm')
        )
```

```{r}
ggsave(filename = "20220420_TAs_IPTG_washout_Plate2_ALL_FIG.png", path = "/Users/halvorsen1/Documents/R_graphs/Washouts", width = 10, height = 2.7, units = "in", device='png', dpi=300)
```

# Import Tse/Col data to combine for Fig. 2 (from 02/25/22)

```{r}

outgrowth <- read_csv(
  "/Users/halvorsen1/Documents/RStudio/csv_files/20220224_IPTG_washout_modifiedImmunities_outgrowth.csv"
)

washout <- read_csv(
  "/Users/halvorsen1/Documents/RStudio/csv_files/20220224_IPTG_washout_modifiedImmunities_washout.csv"
)

keys <- read_plate(
  "/Users/halvorsen1/Documents/RStudio/csv_files/20220224_IPTG_washout_modifiedImmunities_KEYS.csv",
  well_ids_column = "Key"
)

outgrowth <- pivot_longer(outgrowth, cols = A01:E12, names_to = "Key", values_to = "OD600")
washout <- pivot_longer(washout, cols = A01:E12, names_to = "Key", values_to = "OD600")

outgrowth <- full_join(outgrowth, keys, by = "Key")
washout <- full_join(washout, keys, by = "Key")

outgrowth <- outgrowth %>%
  select(-Key, -Replicate, -`cumate (mM)`) %>%
  group_by(Strain, `IPTG (mM)`, Time) %>%
  summarise_at(.vars = "OD600", .funs = c(meanOD = mean, sdOD = sd))

washout <- washout %>%
  select(-Key, -Replicate, -`cumate (mM)`) %>%
  group_by(Strain, `IPTG (mM)`, Time) %>%
  summarise_at(.vars = 'OD600', .funs = c(meanOD = mean, sdOD = sd))

#Reformat time
y <- hms(outgrowth$`Time`)
outgrowth$`Time` <- hour(y) + minute(y) / 60 + second(y) / 360

y <- hms(washout$`Time`)
washout$`Time` <- hour(y) + minute(y) / 60 + second(y) / 360

#washout$`IPTG (μM)` <- as.numeric(washout$`IPTG (μM)`)
washout$Time <- as.numeric(washout$Time)

outgrowth$Time <- round(outgrowth$Time, digits = 2)

washout$Time <- round(washout$Time, digits = 2)

washout2 <- washout
washout2$Time <- washout2$Time + 6.17

coltse_cum <- rbind(washout2, filter(outgrowth, `Time` != 6.17))

```



# Plot Both ColTse (2/25/22) and TA systems (4/20/22) on same graph for Fig. 2
```{r}

plate2_ALL <- rbind(plate2_IPTG, coltse_cum)
plate2_ALL <- filter(plate2_ALL, Strain != "TH245")

strain_names <- as_labeller(c(
                  'TH88' = "CcdB-CcdA",
                  'TH99' = "HicA-HicB",
                  'TH100' = "ParE-ParD",
                  'TH131' = "RelE-RelB",
                  'TH126' = "Tse2-Tsi2",
                  'TH240' = "Tse2-Tsi2[ssrA]",
                  'TH128' = "ColE2-ImmE2",
                  'TH237' = "ColE2-ImmE2[ssrA]"))


discrete_IPTG <- c("#A442C9", "#AC75C1", "#AD8E97", "#C8B09D", "#C2A464", "#DBC873")
plate2_ALL$`IPTG (mM)`<- as.factor(plate2_ALL$`IPTG (mM)`)



plate2_ALL$Strain <- factor(plate2_ALL$Strain, 
                            levels = c("TH88",
                                       "TH99",
                                       "TH100",
                                       "TH131",
                                       "TH126",
                                       "TH240",
                                       "TH128",
                                       "TH237"))

plate2_ALL$Strain <- factor(plate2_ALL$Strain, 
                            levels = c("TH240",
                                       "TH237",
                                       "TH100",
                                       "TH131",
                                       "TH126",
                                       "TH128",
                                       "TH88",
                                       "TH99"))

plate2_ALL %>% 
  #filter(Strain == "TH88" | Strain == "TH99" | Strain == "TH100" | Strain  == "TH131") %>%
  filter(Strain != "TH88" & Strain != "TH99" & Strain != "TH100" & Strain  != "TH131") %>%
  ggplot(aes(x = Time, y = meanOD, color = `IPTG (mM)` , group = `IPTG (mM)`)) +
  facet_wrap(facets = vars(`Strain`), labeller = strain_names, nrow = 2, ncol = 4) +
  geom_rect(xmin=-.3, 
            xmax=5, 
            ymin=-.25, 
            ymax=max(plate2$Time),
            color = NA,
            fill = "gray93", 
            alpha = 0.5) +
  geom_line(size = 0.5) +  
  geom_point(size = 1) +
  geom_errorbar(aes(ymin = meanOD-sdOD, ymax = meanOD+sdOD), width = 0.2) +
  labs(x = 'Time (hrs)', 
       y = expression('OD'[600]),
       color = "IPTG (mM)\nfor 5 hours",
       title = "") +
  scale_x_continuous(limits = c(0,25), breaks = seq(0,25,4)) +
  scale_y_continuous(limits = c(0,1.7), breaks = seq(0,1.7,0.5)) +
  #scale_color_gradient(low = "#DCCC15", 
  #                     high = "#876493",
  #                     guide = "legend", 
  #                     aesthetics = "color", 
  #                     values = cumate_vals,
  #                     na.value = NA) +
  #scale_colour_brewer(palette = "spectral", direction = -1) +
  scale_color_manual(values=discrete_IPTG) +
  # scale_color_manual(values = c("TH88" = "#EC5E8D",
  #                               "TH99" = "#DAA9ED",
  #                              "TH100" = "#E0D935",
  #                              "TH131" = "#F7AB37"),
  #                    labels = strain_names) +
  theme_bw() +
  theme(strip.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(size = 12),
        text = element_text(size = 12),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        plot.title = element_text(size = 13, color = "black", face = "bold"),
        legend.text = element_text(size = 9),
        legend.title = element_text(size = 10),
        strip.text.x = element_text(size = 14),
        legend.key.size = unit(0.4, 'cm')
        )

```


```{r}
ggsave(filename = "20220713_ColTseCircuits_IPTG_Washout.png", path = "/Users/halvorsen1/Documents/R_graphs/Washouts", width = 11, height = 3, units = "in", device='png', dpi=300)
```
6 squares = 14x3
4x2 squares = 11x6 (11.56)