---
title: "Escape mutant seletions on M9 minimal media with alt. carbon sources"
output: pdf_document
---

Each carbon source at 20 mM
Strains were grown for 24 hrs approx. in first round and 20 hrs approx. in 2nd
round

Overnight cultures were grown in 250 uL in 96 deep well plates in Kan20 and 1 mM IPTG

Densities of cultures were not normalized before plating, so may differ in the IPTG condition

```{r echo=FALSE}
library(car)
library(ggplot2)
library(dplyr)
library(plater)
library(tidyverse)
library(lubridate) #hms function
library(reshape2)
library(ggpubr) #pvalues on ggplpots
library(broom)
library(AICcmodavg)
```

```{r echo=FALSE}
CFUs_1 <- read.csv(file = "/Users/halvorsen1/SFA_killswitches/data/escape/20220425_Escapes_MM_all_2_reps.csv")
CFUs_2 <- read.csv(file = "/Users/halvorsen1/SFA_killswitches/data/escape/20220429_Escapes_MM_all_2more_reps.csv")

CFUs_MM <- rbind(CFUs_1, CFUs_2[-9])

std <- function(x) sd(x)/sqrt(length(x))

CFUs_TH86 <- read.csv(file = "/Users/halvorsen1/SFA_killswitches/data/escape/20220420_EscapeFrequencies_SBW25_HST01_IPTG+-.csv")
CFUs_TH86 <-  CFUs_TH86 %>%
  filter(Strain == 'TH86' & Pre_growth == 'IPTG+') %>%
  select(Strain, CFU_perm, CFU_nonperm, Escape_freq, Replicate)

# NORMALIZE COLUMNS TO COMBINE LB AND MM DATASETS FOR PLOTTING INDIVIDUAL DATA POINTS
CFUs_TH86$Media <- 'LB'

CFUs_MM <- CFUs_MM %>%
  select(Strain, CFU_perm, CFU_nonperm, Escape_freq, Media, Replicate)

CFU_MM_merge <- rbind(CFUs_TH86, CFUs_MM)

# ADD IN ssrA TAGGED CIRCUITS

ColTse_Esc_MM <- read_csv(
  "/Users/halvorsen1/SFA_killswitches/data/escape/20220520_ColTse_plusMutants_MinimalMedia_EscapeFrequencies_+IPTG.csv"
)

ColTse_Esc_MM <- ColTse_Esc_MM %>%
  filter(Strain == "TH237" | Strain == "TH240")
ColTse_Esc_MM <- ColTse_Esc_MM %>%
  select(Strain, CFU_perm, CFU_nonperm, Escape_freq, Replicate, Media) 

ColTse_Esc_LB <- read.csv(file = "/Users/halvorsen1/SFA_killswitches/data/escape/20220516_ColTse_plusMutants_EscapeFrequencies_precultureIPTG.csv")

ColTse_Esc_LB <- ColTse_Esc_LB %>%
  filter(Preculture_IPTG == "-") %>%
  filter(Strain == "TH240" | Strain == "TH237")
ColTse_Esc_LB <- ColTse_Esc_LB %>%
  select(Strain, CFU_perm, CFU_nonperm, Escape_freq, Replicate) 

ColTse_Esc_LB$Media <- "LB"

CFU_MM_merge <- rbind(CFUs_MM, ColTse_Esc_MM)

CFU_MM_merge <- rbind(CFU_MM_merge, ColTse_Esc_LB)


# calculate error bars in data frame

# GO BACK INTO CSV FILE AND REPLACE "0" OR NONDETECTABLE REPLICATES WITH 1 COLONY @ LOD AND MAKE NOTE IN A NEW COLUMN THAT IT WAS UNDETECTABLE
CFU_means_log_MM <- CFU_MM_merge %>%
  group_by(Strain, Media) %>%
  summarise(mean = mean(Escape_freq),
            se = std(Escape_freq),
            mean.log = log10(mean(Escape_freq)),
            se.log = log10(std(Escape_freq)),
            pos_std = log10(mean(Escape_freq) + std(Escape_freq)),
            neg_std = log10(mean(Escape_freq) - std(Escape_freq))
  )


CFU_MM_merge$Strain <- factor(CFU_MM_merge$Strain,
                            levels = c("TH86",
                                       "TH88",
                                       "TH99",
                                       "TH100",
                                       "TH131",
                                       "TH126",
                                       'TH240',
                                       "TH128",
                                       "TH237",
                                       "TH98",
                                       "TH124",
                                       "TH214",
                                       "TH203"))


CFU_MM_merge$Media <- factor(CFU_MM_merge$Media, 
                         levels = c("LB",
                                    "Succinate",
                                    "Proline",
                                    "Glucose"))


strain_names <- as_labeller(c('TH37' = "wild type",
                  'TH86' = "regulators\nonly",
                  'TH88' = "CcdB\nCcdA",
                  'TH99' = "HicA\nHicB",
                  'TH100' = "ParE\nParD",
                  'TH98' = "EcoRI\nEcoRIM",
                  'TH124' = "EcoRI (no\nmethylase)",
                  'TH126' = "Tse2\nTsi2",
                  'TH240' = "Tse2\nTsi2-ssrA",
                  'TH128' = "colicin E2\nImmE2",
                  "TH237" = "colicin E2\nImm-ssrA",
                  "TH131" = "RelE\nRelB",
                  "TH203" = "TisB (no\nantitoxin)",
                  "TH214" = "TisB\nIstR2"
                  ))

expSup <- function(w, digits=0) {
  sprintf(paste0("%.", digits, "f*x*10^%d"), w/10^floor(log10(abs(w))), floor(log10(abs(w))))
}

ggplot(CFUs_MM, aes(x = Media, y = Escape_freq, group = Strain, fill = Strain)) +
  stat_summary(fun = "mean", geom = "bar") +
  stat_summary(fun.data = "mean_se", geom = "errorbar") +
  geom_point(size = 0.8) +
  #geom_col(data = CFUs_MM_means, aes(y = meanFreq, x = Media, fill = Strain)) +
  facet_wrap(~Strain, nrow = 11, ncol = 14, labeller = strain_names) +
  labs( y="survival ratio") +
  #geom_errorbar(aes(ymin = meanFreq-stdFreq, ymax = meanFreq+stdFreq), width = 0.4) +
  scale_fill_manual(values = c("TH86" = "gray",
                                "TH88" = "#EC5E8D",
                                "TH99" = "#D7A3EC",
                                "TH100" = "#E0D935",
                                "TH131" = "#F7AB37",
                                "TH126" = "#36D81C",
                                "TH128" = "#4796F5",
                                "TH98" = "#30ECEC",
                                "TH124" = "#30ECEC",
                                "TH203" = "#D4BFDB",
                                "TH214" = "#D4BFDB")) +
  scale_y_log10(
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", scales::math_format(10^.x))) +
  #geom_vline(xintercept = c(5.5, 7.5), size = 0.3) +
  geom_hline(yintercept = 1, color = "black") +
  theme_classic() +
  theme(text = element_text(size = 12),
        strip.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(color = "black", face = "bold", size = 14),
        axis.text = element_text(size = 14), 
        strip.text = element_text(size = 10, angle = 90, vjust = 0.5, hjust = 0.05),
        legend.position = "none",
        legend.title = element_text(size = 12),
        axis.text.x = element_text(size = 12, angle = 90, vjust = 0.5, hjust = 0.95),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 14))
```
```{r echo=FALSE}
ggsave(filename = "20220504_EscapeFrequencies_SBW25_MinimalMedia.png", path = "/Users/halvorsen1/SFA_killswitches/results/figures", width = 7.5, height = 5, units = "in", device='png', dpi=300)
```

Import LB data from 2022 04 20 and select escapees selected from IPTG+ precultures

```{r echo=FALSE}
# RE-PLOT LOG TRANSFORMED DATA ON NORMAL SCALE, OVERLAY DATA POINTS WITH DIFFERENT DATA FRAME

# MAKE PLOT OF ONLY TSE2 and COLICIN FOR FIG. 3

Col_Tse_MM_raw <- filter(.data = CFU_MM_merge, Strain == "TH126" | Strain == "TH128" | Strain == "TH240" | Strain == "TH237")
Col_Tse_MM_means <- filter(.data = CFU_means_log_MM, Strain == "TH126" | Strain == "TH128"| Strain == "TH240" | Strain == "TH237")

Col_Tse_MM_means$Media <- factor(Col_Tse_MM_means$Media,
                               levels = c("LB",
                                          "Succinate",
                                          "Proline",
                                          "Glucose"))

Col_Tse_MM_means$Strain <- factor(Col_Tse_MM_means$Strain,
                               levels = c("TH126",
                                          "TH240",
                                          "TH128",
                                          "TH237"))

Col_Tse_MM_means %>%
  filter(Strain == "TH240") %>%
  filter(Media == "Succinate") %>%
  ggplot() +
  geom_col(mapping = aes(x = Strain, y = mean.log, group = Strain, color = Strain, fill = Strain, size = 0.01), size = 0) +
  #geom_point(data=Col_Tse_MM_raw, mapping = aes(x = Strain, y = log10(Escape_freq), group = Strain), color = "black") +
  #facet_wrap(~ Media, nrow = 11, ncol = 14) +
  labs(y=expression('log'[10]*' survival ratio')) +
  geom_errorbar(mapping=aes(x=Strain,
                             y=mean.log,
                             ymin = neg_std,
                             ymax = pos_std),
                color = "black",
                width = 0.4) +
 scale_fill_manual(values = c(
                   "TH240" = "#A0DA14")) +  
                   # scale_fill_manual(values = c("TH86" = "gray",
  #                               "TH88" = "#EC5E8D",
  #                               "TH99" = "#D7A3EC",
  #                               "TH100" = "#E0D935",
  #                               "TH131" = "#F7AB37",
  #                               "TH126" = "#36D81C",
  #                               "TH240" = "#36D81C",
  #                               "TH128" = "#4796F5",
  #                               "TH237" = "#4796F5",
  #                               "TH98" = "#30ECEC",
  #                               "TH124" = "#30ECEC",
  #                               "TH203" = "#D4BFDB",
  #                               "TH214" = "#D4BFDB")) +
  # scale_color_manual(values = c("TH86" = "gray",
  #                               "TH88" = "#EC5E8D",
  #                               "TH99" = "#D7A3EC",
  #                               "TH100" = "#E0D935",
  #                               "TH131" = "#F7AB37",
  #                               "TH126" = "#36D81C",
  #                               "TH240" = "#36D81C",
  #                               "TH128" = "#4796F5",
  #                               "TH237" = "#4796F5",
  #                               "TH98" = "#30ECEC",
  #                               "TH124" = "#30ECEC",
  #                               "TH203" = "#D4BFDB",
  #                               "TH214" = "#D4BFDB")) +
  # scale_y_log10(
  #   breaks = scales::trans_breaks("log10", function(x) 10^x),
  #   labels = scales::trans_format("log10", scales::math_format(10^.x))) +
  #geom_vline(xintercept = c(5.5, 7.5), size = 0.3) +
  #scale_y_continuous(limits = c(-8.5,2)) +
  scale_y_continuous(limits=c(-7,1), breaks = c(-1,-2,-3,-4,-5,-6,-7)) +
  geom_hline(yintercept = 0.8, color = "black") +
  theme_classic() +
    theme(text = element_text(size = 12),
        panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
        plot.background = element_rect(fill = "transparent", color = NA),
        strip.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(color = "black", face = "bold", size = 14),
        axis.text = element_text(size = 14), 
        strip.text = element_text(size = 12, vjust = -1, hjust = 0.5),
        legend.position = "none",
        legend.title = element_text(size = 12),
        axis.text.x = element_text(size = 12, angle = 90, vjust = 0.5, hjust = 0.95),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 14)
  )
```

```{r echo=FALSE}
ggsave(filename = "20220504_EscapeFrequencies_TH240_Succinate.png", path = "/Users/halvorsen1/SFA_killswitches/results/figures", width = 1, height = 4.2, units = "in", device='png', dpi=300, bg = "transparent")
```

Graph by CFU/mL, as some cultures clearly had a growth defect in IPTG

```{r echo=FALSE}

CFUs_means2 <- CFUs_MM %>%
  group_by(Strain, Media) %>%
  summarise_at(.vars = ('CFU_perm'), .funs = c(meanCFUperm = mean,
                                             stdCFU_perm = std))


CFUs_means2$Strain <- factor(CFUs_means2$Strain,
                            levels = c("TH86",
                                       "TH88",
                                       "TH99",
                                       "TH100",
                                       "TH131",
                                       "TH126",
                                       "TH128",
                                       "TH98",
                                       "TH124",
                                       "TH214",
                                       "TH203"))

CFUs_means2$Media <- factor(CFUs_means2$Media, 
                         levels = c("LB",
                                    "Succinate",
                                    "Proline",
                                    "Glucose"))


ggplot(data = CFU_MM_merge, x = Media, y = CFU_perm) +
  geom_point(aes(x = Media, y = CFU_perm, group = Strain, color = Strain)) +
  facet_wrap(~Strain, nrow = 11, ncol = 14, labeller = strain_names) +
  labs(y="CFU/mL, permissive selection") +
  #geom_errorbar(aes(ymin = meanCFUperm-stdCFU_perm, ymax = meanCFUperm+stdCFU_perm), width = 0.4) +
  stat_summary(aes(x=Media, y=CFU_perm), fun = "mean", geom = "bar") +
  scale_fill_manual(values = c("TH86" = "gray",
                                "TH88" = "#EC5E8D",
                                "TH99" = "#D7A3EC",
                                "TH100" = "#E0D935",
                                "TH131" = "#F7AB37",
                                "TH126" = "#36D81C",
                                "TH128" = "#4796F5",
                                "TH98" = "#30ECEC",
                                "TH124" = "#30ECEC",
                                "TH203" = "#D4BFDB",
                                "TH214" = "#D4BFDB")) +
  scale_y_log10(
    breaks = scales::trans_breaks("log10", function(x) 10^x),
    labels = scales::trans_format("log10", scales::math_format(10^.x))) +
  geom_vline(xintercept = c(5.5, 7.5), size = 0.3) +
  geom_hline(yintercept = 1, color = "black") +
  theme_classic() +
  theme(text = element_text(size = 12),
        strip.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(color = "black", face = "bold", size = 14),
        axis.text = element_text(size = 14), 
        strip.text = element_text(size = 9, angle = 90, vjust = 0.5, hjust = 0),
        legend.position = "none",
        legend.title = element_text(size = 12),
        axis.text.x = element_text(size = 10, angle = 90, vjust = 0.5, hjust = 0.95),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 14)
        )
```

```{r echo=FALSE}
ggsave(filename = "20220504_EscapeFrequencies_SBW25_MinimalMedia_withLB_permissiveCFU.png", path = "/Users/halvorsen1/SFA_killswitches/results/figures", width = 7.5, height = 4, units = "in", device='png', dpi=300)
```

Compute P-value for EcoRI-EcoRIM samples and Tse2-Tsi2/ColE2-ImmE2 samples

To compute student's T test, need to check 3 assumptions:
1. Samples are independent of one another
2. Data from each group follows a normal distribution (test with Shapiro-Wilk test)
3. The two populations have the same variances (test with F-test)

```{r echo=FALSE}
library(rstatix)
CFUs$Media <- 'LB'
CFUs_MM_TH98 <- filter(CFUs_MM, Strain == "TH98")
CFUs_TH98 <- CFUs %>%
  filter(Pre_growth == "IPTG+" & Strain == "TH98") %>%
  select(-Pre_growth, -Species)

CFUs_all_TH98 <- rbind(CFUs_MM_TH98, CFUs_TH98[-c(6)])

CFUs_MM_TH126 <- filter(CFUs_MM, Strain == "TH126")
CFUs_TH126 <- CFUs %>%
  filter(Pre_growth == "IPTG+" & Strain == "TH126") %>%
  select(-Pre_growth, -Species)

CFUs_all_TH126 <- rbind(CFUs_MM_TH126, CFUs_TH126[-c(6)])

CFUs_MM_TH128 <- filter(CFUs_MM, Strain == "TH128")
CFUs_TH128 <- CFUs %>%
  filter(Pre_growth == "IPTG+" & Strain == "TH128") %>%
  select(-Pre_growth, -Species)

CFUs_all_TH128 <- rbind(CFUs_MM_TH128, CFUs_TH128[-c(6)])

#Perform Shapiro-Wilk normality test on each group of samples to determine if they are normally distributed.
#P-value must be greater than 0.05 to imply that the distribution of the data re not significantly
#different from the normal distribution (we can assume normality)

with(CFUs_all_TH98, shapiro.test(Escape_freq[Media == "LB"]))# p = 0.1395
with(CFUs_all_TH98, shapiro.test(Escape_freq[Media == "Succinate"]))# p = 0.2617
with(CFUs_all_TH98, shapiro.test(Escape_freq[Media == "Proline"]))# p = 0.4769
with(CFUs_all_TH98, shapiro.test(Escape_freq[Media == "Glucose"]))# p = 0.7706


# Next perform F-test for homogeneity in variances

CFUs_all_TH98 <- CFUs_all_TH98 %>%
  filter(Media == "LB" | Media == "Glucose")

var.test(Escape_freq ~ Media, data = CFUs_all_TH98) #p = 0.1895, with additional 3 replicates, P-value is now 0.005146

#Between LB and proline F-test resulted in P-value of 0.1895, with additional 3 replicates, P-value is now 0.005146

#Between LB and succinate F-tests resulted in P-value of 0.0007637 which is lower than 0.05, 
# meaning we cannot use classic t-test which assumes equality of the two variances. Will have to
# overcome the violation of this assumption (of homogeneity of variance) by not using the pooled estimate
# for the error term for the t-statistic but instead using an adjustment to the degrees of freedom
# using the Welch-Satterthwaite method (Welch's t-test)


#Between LB and glucose the F-test resulted in P-value of 0.004635, which is lower than the
# significance value of 0.05. Therefore, will have to use Welch's T-test for these samples as well.


# Compute T-test

res <- t_test(CFUs_all_TH98, Escape_freq ~ Media, ref.group = "LB", var.equal = TRUE) 


res_TH98 <- compare_means(Escape_freq ~ Media,  data = CFUs_all_TH98, ref.group = "LB",
              method = "t.test")





# one-way ANOVA tests within each strain across treatments





CFU_MM_merge$Escape_freq <- log10(CFU_MM_merge$Escape_freq)


#Isolate TH88 as a small data frame of groups
TH88 <- filter(.data = CFU_MM_merge, Strain  == "TH88")

#Do not need to perform ANOVA assuming unequal variance
leveneTest(Escape_freq ~ Media, data = TH88)
# P-value 0.6543, proceed with anova
#Perform one-way ANOVA test between means of each group
oneway.test(Escape_freq ~ Media, data = TH88)
# P-value 0.0.04057, significant between media

ttest_88b <- compare_means(Escape_freq ~ Media,  data = TH88,
              method = "t.test")


#Isolate TH99 as a small data frame of groups
TH99 <- filter(.data = CFU_MM_merge, Strain  == "TH99")

#Do not need to perform ANOVA assuming unequal variance
leveneTest(Escape_freq ~ Media, data = TH99)
# P-value 0.5873, proveed with aov()
#Perform one-way ANOVA test between means of each group
oneway.test(Escape_freq ~ Media, data = TH99)

# P-value 0.0695, not significant across media

# Still want to try paired T test
ttest_99 <- compare_means(Escape_freq ~ Media,  data = TH99,
              method = "t.test")
# Proline is significant - Adjusted P-value of 0.035



#Isolate TH100 as a small data frame of groups
TH100 <- filter(.data = CFU_MM_merge, Strain  == "TH100")

# Need to perform ANOVA test with no assumption of equal variance
leveneTest(Escape_freq ~ Media, data = TH100)
# P-value is 0.0001286, so must not assume variance across media is equal

#Perform one-way ANOVA test between means of each group
one.way_100 <- oneway.test(Escape_freq ~ Media, data = TH100)
# nTH100 Results: F = 8.9766, num df = 3.0000, denom df = 5.4376, p-value = 0.01543

# There is significance, so perform paired T-test between individual groups.
ttest_100 <- compare_means(Escape_freq ~ Media,  data = TH100,
              method = "t.test")
# Proline and succinate are significant, with P-values of 0.052 and 0.019, respectively



#Isolate TH131 as a small data frame of groups
TH131 <- filter(.data = CFU_MM_merge, Strain  == "TH131")


# Can assume equal variance
leveneTest(Escape_freq ~ Media, data = TH131)

#Perform one-way ANOVA test between means of each group
one.way_131 <- oneway.test(Escape_freq ~ Media, data = TH131)
summary(one.way_131)

# not significant, but double check with t-test
ttest_131 <- compare_means(Escape_freq ~ Media,  data = TH131,
              method = "t.test")




#Isolate TH98 as a small data frame of groups
TH98 <- filter(.data = CFU_MM_merge, Strain  == "TH98")
leveneTest(Escape_freq ~ Media, data = TH100)
# P value of levene test to test for homogeneity of variance resulted in a significant p value of 0.008011 for TH98.
# Thus, will need to perform an ANOVA test with no assumption of equal variances

# Perform one-way ANOVA test between means of each group,
# no assumption of equal variance
one.way_98 <- oneway.test(Escape_freq ~ Media, data = TH98, var.equal = FALSE)
# Results: F = 6.6117, num df = 3.0000, denom df = 5.6467, p-value = 0.02772

TukeyHSD(aov(Escape_freq ~ Media, data = TH237), conf.level = 0.95)

plot(one.way_98, 2)
with(TH98, t.test(Escape_freq ~ Media))

ttest_98 <- compare_means(Escape_freq ~ Media,  data = TH98, ref.group = "Succinate",
              method = "t.test")

t.test(Escape_freq ~ Media, data = TH98)

ggplot(TH98, aes(x=Replicate, y=log10(Escape_freq))) +
  geom_col()+
  facet_wrap(~Media)


TH214 <- filter(.data = CFU_MM_merge, Strain  == "TH214")
#Isolate TH124 as a small data frame of groups
TH124 <- filter(.data = CFU_MM_merge, Strain  == "TH124")

#Do not need to perform ANOVA assuming unequal variance
leveneTest(Escape_freq ~ Media, data = TH124)
# P-value 0.5873, proveed with aov()
#Perform one-way ANOVA test between means of each group
one.way_124 <- oneway.test(Escape_freq ~ Media, data = TH124, var.equal = FALSE)
summary(one.way_124) 
# P-value 0.0695, not significant across media

# Still want to try paired T test
ttest_124 <- compare_means(Escape_freq ~ Media,  data = TH124, ref.group = "Proline",
              method = "t.test")
# Proline is significant - Adjusted P-value of 0.035



#Isolate TH203 as a small data frame of groups
TH203 <- filter(.data = CFU_MM_merge, Strain  == "TH203")
leveneTest(Escape_freq ~ Media, data = TH203)
# P value = 0.3437, proceed with aov()
one.way_203 <- aov(Escape_freq ~ Media, data = TH203)
summary(one.way_203)
# P value = 0.354, not significant across media
ttest_203 <- compare_means(Escape_freq ~ Media,  data = TH203,
              method = "t.test")

#Isolate TH126 as a small data frame of groups
TH126 <- filter(.data = CFU_MM_merge, Strain  == "TH126")
leveneTest(Escape_freq ~ Media, data = TH126)
# P value = 0.5, proceed with aov()
one.way_126 <- aov(Escape_freq ~ Media, data = TH126)
summary(one.way_126)
# P value - 0.511, not significant across media
ttest_126 <- compare_means(Escape_freq ~ Media,  data = TH126,
              method = "t.test")

#Isolate TH128 as a small data frame of groups
TH128 <- filter(.data = CFU_MM_merge, Strain  == "TH128")
leveneTest(Escape_freq ~ Media, data = TH128)
# P value = 0.572, proceed with aov()
one.way_128 <- aov(Escape_freq ~ Media, data = TH128)
summary(one.way_128)
# P value = 0.572, not significant across media
ttest_128 <- compare_means(Escape_freq ~ Media,  data = TH128,
              method = "t.test")


TH240 <- filter(.data = Col_Tse_MM_raw, Strain == "TH240")
leveneTest(Escape_freq ~ Media, data = TH240)
one.way_240 <- aov(Escape_freq ~ Media, data = TH240)
summary(one.way_240)
# P value 0.0711, not significant across media

TH126_TH240 <- filter(.data = Col_Tse_MM_raw, Strain == "TH240" | Strain == "TH126")

LB <- Col_Tse_MM_raw %>%
  mutate(ID = row_number()) %>%
  #filter(Strain == "TH126" | Strain == "TH240") %>%
  filter(Media == "Succinate")

glucose$Escape_freq <- log10(glucose$Escape_freq)

TukeyHSD(aov((Escape_freq) ~ Strain, data = succinate, conf.level = 0.95))

#with(Col_Tse_MM_raw, group.by = Media, t.test(Escape_freq[Strain == "TH126"], Escape_freq[Strain == "TH240"]))

t_test(data = proline, Escape_freq ~ Strain)

ttest_240_126_glu <- compare_means(data = glucose, Escape_freq ~ Strain,
              method = "t.test")

TH237 <- filter(.data = CFU_MM_merge, Strain == "TH237")
leveneTest(Escape_freq ~ Media, data = TH237)
one.way_237 <- aov(Escape_freq ~ Media, data = TH237)
summary(one.way_237)
# P value of 0.0208, significant across media
```